Perceptions of Corruption in Nigeria

### 2024-11-29 paper/paper.qmd
readme spell check

```{r}
#| include: false
#| warning: false
#| message: false
#| label: setup
#| 
#install.packages("modelsummary")
#install.packages("rstanarm")
#install.packages("dplyr")
#install.packages("here")
#install.packages("arrow")
library(modelsummary)
library(rstanarm)
library(dplyr)
library(here)
library(arrow)
library(bayesplot)
library(ggplot2)
library(arrow)
library(here)

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
#| label: setup

#install.packages("modelsummary")
#install.packages("rstanarm")
#install.packages("dplyr")
#install.packages("here")
#install.packages("arrow")
library(modelsummary)
library(rstanarm)
library(dplyr)
library(here)
library(arrow)
library(bayesplot)
library(ggplot2)
library(arrow)
library(here)
